### 2018-02-19 Sections/cryptowars.tex
QAB figure
QAB, RSA
Finished QAB

@@

@@

@@

@@

@@

@@

@@

Far better than waiting the age of the universe for the right key to turn up, is \textit{cryptanalysis}. Here we study patterns between input and output strings from a cipher utilising a particular key. There are many variations on this, but include techniques such as:
\begin{itemize}
	\item Known plaintext attacks (KPA)\index{Known plaintext attack}: Through alternate means of espionage, the attacker is able to possess \textit{both} a ciphertext and its associated plaintext. Knowing both the input and output to the encryption algorithm may then reveal information about the key.
	\item Chosen plaintext attack (CPA)\index{Chosen plaintext attack}: The same as a KPA except that the adversary has the ability to choose what the known plaintext is.
	\item Linear cryptanalysis\index{Linear cryptanalysis}: A technique for representing ciphers as linear systems, to which KPA are applied.
	\item Differential cryptanalysis\index{Differential cryptanalysis}: We analyse how changes in input bits propagate through the cipher to modulate output bits. Typically this type of technique operates as a CPA.
\end{itemize}

@@

@@

@@

@@

@@

%
% BB84 & E91 Protocols
%

\paragraph{BB84 \& E91 protocols}\index{BB84 protocol}\index{E91 protocol}

@@

E91 is slightly different. Here Alice and Bob share an entangled Bell-pair provided by a central authority. Then both Alice \textit{and} Bob measure their qubits in random bases. As with BB84, after measuring all qubits, they compare their choices of random bases. When they coincide, they have a shared bit. When they don't, they discard their result. From here the remainder of the protocol is the same as for BB84.

@@

@@

@@

\cite{Wehner}

\comment{Ryan TO DO}

\comment{Talk about Wehner scheme, as well as Brennen/Menicucci toric code scheme.}

>>>>

%
% Classical Cryptography
%

@@

%
% Private-Key Cryptography
%

@@

%
% Public-Key Cryptography
%

@@

\begin{table}[!htb]
\fbox{\parbox{0.965\columnwidth}{\texttt{ 
function RSAEncrypt(plaintext, publicKey):
\begin{enumerate}
\item 
\item $\Box$
\end{enumerate}
function RSADecrypt(ciphertext, privateKey):
\begin{enumerate}
\item 
\item $\Box$
\end{enumerate}
}}}
\caption{} \label{alg:RSA}
\end{table}

%
% Attacks On Classical Cryptography
%

@@

%
% Classical Attacks
%

@@

%
% Brute-Force
%

@@

%
% Cryptanalysis
%

@@

Far better than waiting the age of the universe for the right key to turn up, is \textit{cryptanalysis}. Here we study patterns between input and output strings from a cipher utilising a particular key. There are many variations on this, but include techniques such as \cite{bib:Schneier}:
\begin{itemize}
	\item Known plaintext attacks (KPA)\index{Known plaintext attack}: Through alternate means of espionage, the attacker is able to possess \textit{both} a ciphertext and its associated plaintext. Knowing both the input and output to the encryption algorithm may then reveal information about the key.
	\item Chosen plaintext attack (CPA)\index{Chosen plaintext attack}: The same as a KPA except that the adversary has the ability to choose what the known plaintext is.
	\item Linear cryptanalysis\index{Linear cryptanalysis}: A technique for representing ciphers as linear systems, to which KPA are applied.
	\item Differential cryptanalysis\index{Differential cryptanalysis}: We analyse how changes in input bits propagate through the cipher to modulate output bits. Typically this type of technique operates as a CPA.
\end{itemize}

%
% Integer Factorisation
%

@@

%
% Quantum Attackes
%

@@

%
% Integer Factorisation
%

@@

%
% The Blockchain
%

@@

%
% The End Of Classical Cryptography?
%

@@

%
% BB84 Protocol
%

\paragraph{BB84 protocol}\index{BB84 protocol}

@@

%
% E91 Protocol
%

\paragraph{E91 protocol}\index{E91 protocol}

E91 is slightly different to BB84. Here Alice and Bob share an entangled Bell-pair provided by a central authority. Then both Alice \textit{and} Bob measure their qubits in random bases. As with BB84, after measuring all qubits, they compare their choices of random bases. When they coincide, they have a shared bit. When they don't, they discard their result. From here the remainder of the protocol is the same as for BB84.

@@

%
% Security
%

\paragraph{Security}\index{Security of QKD}

@@

%
% Hybrid Quantum/Classical Cryptography
%

@@

The previously described protocols all focussed on preserving the secrecy of messages. Alternately, it may not be the message that is sensitive, but rather the identity of the person who says it. \textit{Anonymous broadcasting}\index{Anonymous broadcasting} is a protocol for achieving this.

Consider the following scenario. A group of users share a classical broadcast channel that anyone is able to transmit to, and everybody is able to listen to unencrypted. But it is of importance that the identity of whoever broadcasts to the channel must be kept secret to all users. \cite{Wehner} described a scheme for achieving this quantum mechanically using shared GHZ states -- \textit{quantum anonymous broadcasting} (QAB).

Let there be a (trusted) server that distributes GHZ states (of arbitrary numbers of qubits) to a group of users, one qubit per user. This can be prepared as described in, for example, Sec.~\ref{sec:GHZ_states}. Now if every user measures in the \mbox{$\ket\pm=\frac{1}{\sqrt{2}}(\ket{0}+\ket{1})$} basis the joint \textit{parity} (i.e whether an even or odd number of $+$'s were measured) is guaranteed to be even. For example, all users might measure $\ket{+}\bra{+}$, or exactly 2, but never exactly 1 or 3.

On the other hand, if a $\hat{Z}$ gate were applied to any one qubit, this would flip the parity outcome. Note that a GHZ transforms according to,
\begin{align}
	\hat{Z}_i \frac{1}{\sqrt{2}}(\ket{0}^{\otimes n} + \ket{1}^{\otimes n}) \to \frac{1}{\sqrt{2}}(\ket{0}^{\otimes n} - \ket{1}^{\otimes n}),
\end{align}
for any qubit $i$. This invariance in the location of the $\hat{Z}$ gate is the basis for the anonymity of the protocol. If a user wishes to broadcast `0' he does nothing, whereas if we wishes to broadcast `1' he applies the $\hat{Z}$ gate to his local qubit.

Finally, all users measure their qubits in the $\pm$-basis and publicly (without encryption) broadcast their measurement outcomes. All users now see all other users' measurement outcomes and are able to calculate the collective parity of the measurements. Now if the parity is even, the speaker must have said `0', whereas if it is odd he must have said `1'. The protocol is shown in Fig.~\ref{fig:QAB} and described in detail in Alg.~\ref{alg:QAB}

\begin{figure}[!htb]
\includegraphics[width=0.47\textwidth]{QAB}
\caption{Protocol for quantum anonymous broadcasting. (a) A central trusted server prepares GHZ states and distributes them amongst a group of users, one qubit per user. All uses measure in the $\pm$-basis. (b) All users classically broadcast their measurement outcomes yielding shared random parity. During broadcast, the broadcaster lies about his measurement outcome to flip the joint parity if he wishes to transmit `1', or tells the truth to transmit `0'. The joint parity encodes the message of the anonymous user, which all listeners are able to recover.} \label{fig:QAB}	
\end{figure}

\begin{table}[!htb]
\fbox{\parbox{0.965\columnwidth}{\texttt{ 
function QuantumAnonymousBroadcasting(message, speaker):
\begin{enumerate}
\item $\ket\psi = \ket{\mathrm{GHZ}}$
\item $\ket\psi \to (\hat{Z}_\mathrm{speaker})^\mathrm{message}\ket\psi$
\item for(i$\in$users) \{
	\setlength{\itemindent}{.2in}
\item outcome$_i$ = measureInXBasis($\ket\psi_\mathrm{i}$)
\setlength{\itemindent}{0in}
\item \}
\item parity = \big($\sum_i$ outcome$_i$\big)\,mod\,2
\item return(parity)
\item $\Box$
\end{enumerate}
}}}
\caption{Protocol for quantum anonymous broadcasting. The GHZ state is distributed in advance, one qubit per user. The measurement outcomes are classically broadcast without encryption. The final parity of the classical measurements reflects the message bit without identifying the speaker.} \label{alg:QAB}
\end{table}

Note that the scheme can be slightly simplified by rather than the speaker applying the $\hat{Z}$ to his qubit, upon announcing his measurement outcome he instead lies about his outcome and flips it. This follows simply because a $\hat{Z}$ gate prior to a $\pm$ measurement bit flips the classical measurement outcome, \mbox{$\hat{Z}\ket\pm=\ket\mp$}.

There are no constraints on time ordering of the measurements, nor, much like BB84, are there any interferometric requirements (not including the GHZ preparation stage), making this protocol very experimentally practical over long distances.

Because of the time invariance in the measurements, distribution and measurement of the GHZ states can be performed well in advance of the actual message broadcast. This allows us to treat `shared parity'\index{Shared parity} as a fundamental resource (Sec.~\ref{sec:ent_ultimate}) for the QAB cryptoprotocol.

Since the parity-sharing can be isolated from the broadcasting stage it is unimportant if the GHZ source is non-deterministic or the channels for distributing it lossy. We can instead simply repeat GHZ distribution over and over at high repetition rate, post-selecting upon measurement outcomes where all users signal that they successfully received and measured their photons.

For these reasons, this scheme lends itself readily to photonic implementation, provided a reliable GHZ preparation circuit. The scheme has since been ported to operate on toric codes\index{Toric code} to facilitate error correction of the distributed GHZ states.
